Distortion-corrected kernel density estimate on Riemannian manifolds

### 2022-10-10 paper/paper.Rmd
Change load file name

```{r fivedcors, echo=FALSE, message=FALSE, eval=T}
load("figures/CorrelationTable_4d_N10000_4ml_radius10_r1.rda")
col.max <- apply(cors, 2, max)
max.match <- rep(col.max, each = 2) == cors
data.frame(cors) %>% 
  mutate_if(is.numeric, format, digits = 3, nsmall = 3) %>% 
  kableExtra::kbl(caption = "Correlation between true density and estimated density for four manifold learning embeddings.", booktabs = TRUE, digits = 3, escape = FALSE) %>%
  # kable_styling(latex_options = "scale_down") %>% # automatically adjust the table to page width
  kable_paper(full_width = FALSE) %>%
  # column_spec(1, width = "6cm") %>% 
  column_spec(2, bold = max.match[,1]) %>%
  column_spec(3, bold = max.match[,2]) %>%
  column_spec(4, bold = max.match[,3]) %>%
  column_spec(5, bold = max.match[,4])
```
```{r fourdhdrtable, echo=FALSE, message=FALSE, eval=T}
load("figures/HDRTable_4d_N10000_4ml_radius10_r1.rda")
hdrtable %>% 
  kableExtra::kbl(caption = "Percentage comparison of correct highest density regions in density estimation of four manifold learning embeddings.", booktabs = TRUE, digits = 3, escape = FALSE, align = "c",
                  col.names = c(rep(c("DC-KDE", "KDE"), 4))
                  ) %>%
  # kable_classic("striped") %>% 
  kable_styling(latex_options = "scale_down") %>%
  kable_paper(full_width = FALSE) %>%
  # add_header_above(c("HDRs" = 1, rep(c("DC-KDE" = 1, "KDE" = 1), 4))) %>%
  add_header_above(c(" " = 1, "ISOMAP" = 2, "LLE" = 2, "Laplacian Eigenmaps" = 2, "UMAP" = 2)) %>% 
  # column_spec(1, bold = TRUE) %>% 
  column_spec(2, bold = hdrmax[,1]) %>% 
  column_spec(3, bold = hdrmax[,2]) %>% 
  column_spec(4, bold = hdrmax[,3]) %>% 
  column_spec(5, bold = hdrmax[,4]) %>% 
  column_spec(6, bold = hdrmax[,5]) %>% 
  column_spec(7, bold = hdrmax[,6]) %>% 
  column_spec(8, bold = hdrmax[,7]) %>% 
  column_spec(2*(1:4), border_left = T, background = grey(0.9))
```

>>>>

```{r fivedcors, echo=FALSE, message=FALSE, eval=T}
load("figures/CorrelationTable_4d_N10000_4ml_radius10_r1.rda")
col.max <- apply(cors, 2, max)
max.match <- rep(col.max, each = 2) == cors
data.frame(cors) %>% 
  mutate_if(is.numeric, format, digits = 3, nsmall = 3) %>% 
  kableExtra::kbl(caption = "Correlation between true density and estimated density for four manifold learning embeddings.", booktabs = TRUE, digits = 3, escape = FALSE) %>%
  # kable_styling(latex_options = "scale_down") %>% # automatically adjust the table to page width
  kable_paper(full_width = FALSE) %>%
  # column_spec(1, width = "6cm") %>% 
  column_spec(2, bold = max.match[,1]) %>%
  column_spec(3, bold = max.match[,2]) %>%
  column_spec(4, bold = max.match[,3]) %>%
  column_spec(5, bold = max.match[,4])
```
```{r fourdhdrtable, echo=FALSE, message=FALSE, eval=T}
load("figures/hdrtable_4d_N10000_4ml_radius10_r1.rda")
hdrtable %>% 
  kableExtra::kbl(caption = "Percentage comparison of correct highest density regions in density estimation of four manifold learning embeddings.", booktabs = TRUE, digits = 3, escape = FALSE, align = "c",
                  col.names = c(rep(c("DC-KDE", "KDE"), 4))
                  ) %>%
  # kable_classic("striped") %>% 
  kable_styling(latex_options = "scale_down") %>%
  kable_paper(full_width = FALSE) %>%
  # add_header_above(c("HDRs" = 1, rep(c("DC-KDE" = 1, "KDE" = 1), 4))) %>%
  add_header_above(c(" " = 1, "ISOMAP" = 2, "LLE" = 2, "Laplacian Eigenmaps" = 2, "UMAP" = 2)) %>% 
  # column_spec(1, bold = TRUE) %>% 
  column_spec(2, bold = hdrmax[,1]) %>% 
  column_spec(3, bold = hdrmax[,2]) %>% 
  column_spec(4, bold = hdrmax[,3]) %>% 
  column_spec(5, bold = hdrmax[,4]) %>% 
  column_spec(6, bold = hdrmax[,5]) %>% 
  column_spec(7, bold = hdrmax[,6]) %>% 
  column_spec(8, bold = hdrmax[,7]) %>% 
  column_spec(2*(1:4), border_left = T, background = grey(0.9))
```
